\documentclass[twocolumn]{elsarticle}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}

\begin{frontmatter}

\title{Title of Your Research Paper}

\author[inst1]{Your Name}
\author[inst2]{Co-author Name}
\affiliation[inst1]{organization={Your Institution}, addressline={Address Line}, city={City}, postcode={Postal Code}, country={Country}}
\affiliation[inst2]{organization={Co-author Institution}, addressline={Address Line}, city={City}, postcode={Postal Code}, country={Country}}

\begin{abstract}
    The abstract should briefly summarize the key points of the paper, including the problem, your approach, and main results.
\end{abstract}

\begin{keyword}
    Keywords \sep Should \sep Be \sep Listed \sep Here
\end{keyword}

\end{frontmatter}

\section{Introduction}
\label{sec:intro}
Introduce the problem, its importance, and the current state of the art. Mention the gaps in the existing literature and how your proposed algorithm addresses these gaps.

\section{Related Work}
\label{sec:related}
Review the literature on related algorithms and techniques. Highlight the strengths and weaknesses of each and set the stage for your contribution.

\section{Proposed Algorithm}
\label{sec:algorithm}
Describe your algorithm in detail. Include pseudo-code, flowcharts, or any other illustrations that help explain the algorithm.

\subsection{Algorithm Description}
Provide a step-by-step description of your algorithm.

\subsection{Complexity Analysis}
Analyze the time and space complexity of your algorithm.

\section{Experimental Setup}
\label{sec:setup}
Describe the experimental setup, including the datasets used (e.g., CEC13 and Engineering problem set), the evaluation metrics, and the computational environment.

\section{Results and Discussion}
\label{sec:results}
Present the results of your experiments. Use tables and figures to compare the performance of your algorithm with the 10 previous algorithms.

\subsection{Benchmark Functions}
Discuss the performance on CEC13 benchmark functions.

\subsection{Engineering Problem Set}
Discuss the performance on the Engineering problem set.

\subsection{Comparison with Other Algorithms}
Compare your results with those of 10 previous algorithms. Highlight where your algorithm excels and where it might need improvement.

\section{Conclusion}
\label{sec:conclusion}
Summarize the key findings of your research. Discuss the implications of your results and suggest possible directions for future work.

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{your-bibliography-file}

\end{document}
